### 2022-03-27 chapters/intro/intro.tex
modif post-defense part II²

\modif{new paragraph: Eulerian vs Lagrangian and why Lagrangian} In this study, coral larvae were modeled using a Lagrangian particle tracking model forced by SLIM currents. To answer our different research questions, we adapted this larval transport model to evaluate the dispersal of the causative agent of the SCTLD and sediments particles. \modif{[add stuff about the bathymetry and the model validation]}

>>>>

\modif{Transport processes are at the core of this thesis. They can be estimated using two general methods: Eulerian tracers and Lagrangian particles. Eulerian methods were the earliest methods applied for transport modeling and are still widely used today. They offer the advantages of a fixed grid by solving the transport equations directly on the native grid of the model and are easy to implement However, mass conservation issues may arise in problems with high initial gradient of concentrations \citep{spivakovskaya2007lagrangian}. The Lagrangian methods, on the other hand, follow virtual particles of zero spatial extent whose movements are modeled with a stochastic differential equation consistent with the advection-diffusion equation \citep{spivakovskaya2007lagrangian,van2018lagrangian}. One key difference between the two  methods is their computational cost. For each time step, the movements of $N$ virtual particles require $N$ sets of computation, while the advection-diffusion of a tracer takes as many sets of computation as there are discrete grid cells in the model. Additionally, Lagrangian methods allow the storage of the entire trajectory history of the virtual particles. This enables the \textit{a posteriori} computation of connectivity between different regions of the ocean \citep{thomas2014numerical,frys2020fine}. Furthermore, particles can be advected in offline mode when velocity fields are stored in order to reduce computation time, while Eulerian tracers' equations must be solved online with the current velocities. Finally, Lagrangian particles can be advected backward in time. This reverse-time analysis gives a spatial probability distribution of places from where it is likely that particles originated to reach a given location \citep{spivakovskaya2005simulation}. Transport processes were therefore studied in this thesis using Lagrangian particles advected by SLIM currents. To answer our different research questions, we adapted SLIM transport model to evaluate the dispersal of the causative agent of the SCTLD and sediments particles.}
